---
title: "CBAMM: An R Package for Collaborative Bayesian Adaptive Meta-Analysis Methods"
author: "Mahmood Ahmad"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{CBAMM Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(cbamm)
```

## Introduction

The `cbamm` package provides a unified framework for modern meta-analysis, focusing on three key innovations:

1.  **Sequential Evidence Monitoring:** Using Trial Sequential Analysis (TSA) to prevent false-positive conclusions in living systematic reviews.
2.  **Population Transportability:** Using entropy balancing to weight meta-analytic evidence toward a target population's characteristics.
3.  **Automated Decision Support:** Translating statistical results into clinical, statistical, and methodological "personas."

## Case Study 1: Sequential Evidence Monitoring

We demonstrate sequential monitoring using the classic **BCG Vaccine** dataset (13 studies on vaccine effectiveness against TB).

```{r bcg_example}
# Load BCG data
data(bcg_data)

# Run cumulative meta-analysis with TSA
# We'll set an alternative effect of -0.5 (clinically meaningful RR = 0.6)
cum_res <- cumulative_meta_analysis(
  bcg_data,
  order_by = "year",
  tsa_effect_alt = -0.5,
  tsa_alpha = 0.05,
  tsa_beta = 0.20
)

# Print cumulative results with Multi-Persona Review
print(cum_res)
```

In this analysis, the multi-persona review summarizes whether the evidence has reached sufficiency (using TSA boundaries) and stability (using the point where the estimate stop fluctuating).

## Case Study 2: Population Transportability

Meta-analysis results are often a "one-size-fits-all" estimate. `cbamm` allows us to weight studies based on how well they match a **target population**.

Assume we have a target population that is older and has a higher BMI than the studies in our meta-analysis.

```{r transport_example}
# Load simulated meta-analysis data
data(example_meta)

# Define our target population characteristics
target_pop <- list(
  age_mean = 65,     # Older than the average study (approx. 55)
  female_pct = 0.45,
  bmi_mean = 31,     # Higher BMI than the average study (approx. 27)
  charlson = 3.5     # Higher comorbidity
)

# Compute transport weights using entropy balancing
weights <- compute_transport_weights(example_meta, target_pop)

# The weights adjust the contribution of each study to match the target
# Run weighted meta-analysis (simplified example using the weights)
# In practice, we use these weights to adjust the 'precision' or 'vi'
example_meta$weights <- weights
weighted_res <- cbamm_fast(example_meta) # Note: Internal implementation uses weights if provided

# Compare with original unweighted estimate
unweighted_res <- cbamm_fast(example_meta)

cat("Unweighted estimate: ", round(unweighted_res$b, 3), "\n")
cat("Weighted (Transported) estimate: ", round(weighted_res$b, 3), "\n")
```

## Case Study 3: Bayesian Meta-Analysis with Bayes Factors

`cbamm` provides a Gibbs sampler to estimate the posterior of the overall effect and heterogeneity.

```{r bayesian_example}
# Run Bayesian random-effects meta-analysis
bayesian_res <- cbamm_bayesian(bcg_data, n_iter = 5000)

# Print results including Bayes Factors (BF10)
print(bayesian_res)
```

The **BF10** tells us the strength of evidence in favor of the effect hypothesis vs. the null. A BF10 > 10 is considered strong evidence.

## Conclusion

`cbamm` bridges the gap between complex statistical synthesis and clinical interpretation. By incorporating transportability and sequential monitoring, it provides a more robust and personalized evidence base for medical decision-making.
